---
title: "Interpretability_Pres_Plots"
output:
  html_document: default
  pdf_document: default
---


## Loading Libraries

```{r, results='hide', message=FALSE, warning=FALSE}
library("tidyverse")
library("rpart")
library("rpart.plot")
library("rlist")
library("gridExtra")
library("randomForest")
library("gbm")
library("mgcv")
library("pdp")
library("ALEPlot")
library("lime")
library("iml")
```

# Background

## Generating Data

```{r}
set.seed(4321)
num_samples = 1000
x = sort(rnorm(num_samples))
eps = rnorm(1000, sd = 1.5)
y = 4 - 2 * x + 0.5 * sin(pi * x) + eps
y = (y - mean(y)) / sd(y)
sim_data = data.frame(y, x)
```

## Linear Model

```{r}

reg_model = lm(y ~ x, data = sim_data)
y_hat = predict(reg_model, sim_data)
pred_data = data.frame(y_hat,x)


ggplot(data = sim_data, aes(y = y,x = x)) + 
  geom_point() +
  geom_line(data = pred_data,
            aes(y = y_hat,x = x),
            colour = "red",
            size = 1) +
  theme_bw(base_size = 25)  

```

## Decision Tree

```{r}

tree_model = rpart(y ~ x, data = sim_data)
y_hat = predict(tree_model, sim_data)
pred_data = data.frame(y_hat,x)


ggplot(data = sim_data, aes(y = y,x = x)) + 
  geom_point() +
  geom_line(data = pred_data,
            aes(y = y_hat,x = x),
            colour = "red",
            size = 1) +
  theme_bw(base_size = 25)  

```

```{r}

rpart.plot(tree_model)

```

## Random Forest

```{r}
set.seed(8675309)
forest_model = randomForest(y ~ x, data = sim_data, ntree = 500, maxnodes = 10)
y_hat = predict(forest_model, sim_data)
pred_data = data.frame(y_hat,x)


ggplot(data = sim_data, aes(y = y,x = x)) + 
  geom_point() +
  geom_line(data = pred_data,
            aes(y = y_hat,x = x),
            colour = "red",
            size = 1) +
  theme_bw(base_size = 25)  

```

## Synthetic Data

```{r}
set.seed(90210)
num_samples = 500
x1 = rnorm(num_samples)
x2 = rnorm(num_samples)
x3 = rnorm(num_samples)
x4 = rnorm(num_samples)
eps = rnorm(1000, sd = 3)
y = 4 * x1 - 2 * sin(pi*x2) + 3 * x3^2 + abs(x4) + eps
y = (y - mean(y)) / sd(y)
sim_data = data.frame(y, x1, x2, x3, x4)
```

## Plotting

```{r}

p1 = qplot(x1,y,data=sim_data) + theme_bw(base_size = 15)
p2 = qplot(x2,y,data=sim_data) + theme_bw(base_size = 15)
p3 = qplot(x3,y,data=sim_data) + theme_bw(base_size = 15)
p4 = qplot(x4,y,data=sim_data) + theme_bw(base_size = 15)
grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2)

```

## GAM Model

```{r}

set.seed(1234)
gam_model = gam(y ~ x1 + s(x2) + s(x3) + s(x4), data = sim_data)

```

## Plot Predictions wrt All Variables

```{r}
y_hat = predict(gam_model)
pred_data = data.frame(y_hat,x1,x2,x3,x4)

double_plot = function(var_name,size=15) {
  plot = ggplot(data=sim_data,aes_string(x=var_name,y="y")) +
    geom_point() +
    geom_point(data=pred_data,aes_string(x=var_name,y="y_hat"),colour="red") +
    theme_bw(base_size=size)
  return(plot)
}


p1 = double_plot("x1")
p2 = double_plot("x2")
p3 = double_plot("x3")
p4 = double_plot("x4")
grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2)

```

# ICE

## Inspect x3

```{r}

ggplot(data=sim_data,aes(x=x3,y=y)) +
  geom_point(size=2) +
  geom_point(data=pred_data,aes(x=x3,y=y_hat),colour="red",size=2) +
  theme_bw(base_size=25)

```

## Single Observation

```{r}

ggplot(data=sim_data,aes(x=x3,y=y)) +
  geom_point(size=2, alpha=0.1) +
  geom_point(data=pred_data,aes(x=x3,y=y_hat),colour="red",size=2, alpha=0.1) +
  geom_point(data=sim_data[1,],aes(x=x3,y=y),size=5) +
  geom_point(data=pred_data[1,],aes(x=x3,y=y_hat),colour="red",size=5) +
  theme_bw(base_size=25)

```

```{r}

single_obs = pred_data[1,]
write.table(single_obs, "clipboard", sep="\t", row.names=FALSE)

x3_values = seq(-3,3,1)
rep_obs = single_obs[rep(1,length(x3_values)),]
rep_obs$x3 = x3_values
rep_obs$yhat = predict(gam_model,rep_obs)
write.table(rep_obs, "clipboard", sep="\t", row.names=FALSE)

```

## ICE for Observation 1

```{r}

x3_grid = seq(min(x3),max(x3),0.1)
ice_data = sim_data[rep(1,length(x3_grid)),]
ice_data$x3 = x3_grid
ice_data$y_hat = predict(gam_model, ice_data)

ggplot(data=sim_data,aes(x=x3,y=y)) +
  geom_point(size=2, alpha=0.1) +
  geom_point(data=pred_data,aes(x=x3,y=y_hat),colour="red",size=2, alpha=0.1) +
  geom_point(data=sim_data[1,],aes(x=x3,y=y),size=5) +
  geom_point(data=pred_data[1,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=ice_data,aes(x=x3,y=y_hat),colour="red",size=1) +
  theme_bw(base_size=25)

```

## More ICE!

```{r}

x3_ice = function(model,obs) {
  x3_grid = seq(min(x3),max(x3),0.1)
  ice_data = sim_data[rep(obs,length(x3_grid)),]
  ice_data$x3 = x3_grid
  ice_data$y_hat = predict(model, ice_data)
  return(ice_data)
}

ggplot(data=sim_data,aes(x=x3,y=y)) +
  geom_point(size=2, alpha=0.1) +
  geom_point(data=pred_data,aes(x=x3,y=y_hat),colour="red",size=2, alpha=0.1) +
  geom_point(data=sim_data[1,],aes(x=x3,y=y),size=5) +
  geom_point(data=pred_data[1,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(gam_model,1),aes(x=x3,y=y_hat),colour="red",size=1) +
  geom_point(data=pred_data[2,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(gam_model,2),aes(x=x3,y=y_hat),colour="red",size=1) +
  geom_point(data=pred_data[3,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(gam_model,3),aes(x=x3,y=y_hat),colour="red",size=1) + 
  geom_point(data=pred_data[4,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(gam_model,4),aes(x=x3,y=y_hat),colour="red",size=1) + 
  geom_point(data=pred_data[5,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(gam_model,5),aes(x=x3,y=y_hat),colour="red",size=1) +
  theme_bw(base_size=25)

```

## More ICE, Forest

```{r}
set.seed(1234)
forest_model = randomForest(y ~ x1 + x2 + x3 + x4,data=sim_data)
forest_pred_data = pred_data
forest_pred_data$y_hat = predict(forest_model,forest_pred_data)

ggplot(data=sim_data,aes(x=x3,y=y)) +
  geom_point(size=2, alpha=0.1) +
  geom_point(data=forest_pred_data,aes(x=x3,y=y_hat),colour="red",size=2, alpha=0.1) +
  geom_point(data=sim_data[1,],aes(x=x3,y=y),size=5) +
  geom_point(data=forest_pred_data[1,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(forest_model,1),aes(x=x3,y=y_hat),colour="red",size=1) +
  geom_point(data=forest_pred_data[2,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(forest_model,2),aes(x=x3,y=y_hat),colour="red",size=1) +
  geom_point(data=forest_pred_data[3,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(forest_model,3),aes(x=x3,y=y_hat),colour="red",size=1) + 
  geom_point(data=forest_pred_data[4,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(forest_model,4),aes(x=x3,y=y_hat),colour="red",size=1) + 
  geom_point(data=forest_pred_data[5,],aes(x=x3,y=y_hat),colour="red",size=5) +
  geom_line(data=x3_ice(forest_model,5),aes(x=x3,y=y_hat),colour="red",size=1) +
  theme_bw(base_size=25)

```

# Partial Dependence

```{r}

write.table(pred_data[1:7,], "clipboard", sep="\t", row.names=FALSE)

ex_data = pred_data[1:7,]
ex_data$x3 = 0
ex_data$y_hat = predict(gam_model, ex_data)


```

## Plot PD

```{r}

pd_data = partial(gam_model,pred.var = "x3", pred.grid = data.frame(x3=c(-3,-2,-1,0,1,2,3)))
write.table(pd_data[1:7,], "clipboard", sep="\t", row.names=FALSE)

pd_data = partial(gam_model,pred.var = "x3", plot.engine = "ggplot2")

ggplot(data=sim_data,aes(x=x3,y=y)) + 
  geom_point(size=2, alpha=0.1) +
  geom_point(data=pred_data,aes(x=x3,y=y_hat),colour="red",size=2, alpha=0.1)  +
  geom_line(data=pd_data,aes(x=x3,y=yhat),colour="red",size=1) +
  theme_bw(base_size=25)

```

## All of the Partial Dependences

```{r}

pd_plot = function(model,var_name) {
  plot_data = partial(model,pred.var = var_name, plot.engine = "ggplot2")
  plot = ggplot(data=plot_data,aes_string(x=var_name,y="yhat")) +
    geom_line(colour="red",size=1) +
    theme_bw(base_size = 20)
  return(plot)
}

p1 = pd_plot(gam_model,"x1")
p2 = pd_plot(gam_model,"x2")
p3 = pd_plot(gam_model,"x3")
p4 = pd_plot(gam_model,"x4")

grid.arrange(p1,p2,p3,p4)


```

## ALL PD, Forest

```{r}

p1 = pd_plot(forest_model,"x1")
p2 = pd_plot(forest_model,"x2")
p3 = pd_plot(forest_model,"x3")
p4 = pd_plot(forest_model,"x4")

grid.arrange(p1,p2,p3,p4)

```

## 2-Way Partial Dependence

```{r}

plot_data = partial(gam_model,pred.var = c("x2","x4"))
ggplot(data=plot_data,aes(x=x2,y=x4,z=yhat,fill=yhat)) +
  geom_raster() +
  scale_fill_gradientn(colours=c("red","white")) +
  theme_bw(base_size = 20)

```

# LIME

## Setup Models in LIME

```{r}


model_type.gam = function(x, ...) { return("regression") }

predict_model.gam = function(x, newdata, ...) {
  pred = predict(x, newdata)
  return(as.data.frame(pred))
}

model_type.randomForest = function(x, ...) { return("regression") }

predict_model.randomForest = function(x, newdata, ...) {
  pred = predict(x, newdata)
  return(as.data.frame(pred))
}

```

## Some LIME examples

```{r}

explainer = lime(sim_data,model = gam_model, bin_continuous = FALSE,use_density = FALSE)
gam_explanations = explain(sim_data[1:4,c("x1","x2","x3","x4")],explainer,n_features = 4)

plot_features(gam_explanations, ncol = 2)
gam_explanations

```

## Plot LIME

```{r}

lime_line = function(model,data,point,feature) {

  explainer = lime(data,model = model, bin_continuous = FALSE)
  explanations = explain(data[point,c("x1","x2","x3","x4")],explainer,n_features = 4)
  
  intercept = explanations[explanations$feature == feature,"model_prediction"][[1]]
  slope = explanations[explanations$feature == feature,"feature_weight"][[1]]
  
  plot_domain = seq(min(sim_data[,feature]),max(sim_data[,feature]),0.1)
  exp_pred = (plot_domain - data[point,feature]) * slope + intercept

  out = data.frame(feature = plot_domain, "yhat" = exp_pred)
  names(out)[names(out) == "feature"] = feature

  return(out)
}

plot_pd_lime = function(model, data, point, feature, alpha, plot_point, plot_lime) {
  
  pred_data = data
  pred_data[,"yhat"] = predict(model,data)

  partial_data = partial(model,pred.var = feature, plot.engine = "ggplot2")
  partial_span = max(partial_data$yhat) - min(partial_data$yhat)
  
  plot = ggplot(data=partial_data,aes_string(x=feature,y="yhat"),size=2) +
    geom_line(size=1) +
    geom_point(data=pred_data,aes_string(x=feature,y="yhat"),colour="red",alpha=alpha) +
    ylim(min = min(partial_data$yhat,pred_data[point,"yhat"]) - 0.5*partial_span, 
         max = max(partial_data$yhat,pred_data[point,"yhat"]) + 0.5*partial_span) +
    theme_bw(base_size = 20)
  
  if (plot_point) {
    plot = plot + geom_point(data=pred_data[point,],aes_string(x=feature,y="yhat"))
  }
  
  if (plot_lime) {
    plot = plot + geom_line(data=lime_line(model, data, point, feature), aes_string(x=feature,y="yhat"), 
                            color = "red",size = 1)
  }
  
  return(plot)
}

point = 1
p1 = plot_pd_lime(gam_model, sim_data, point, "x1", 0, FALSE, FALSE)
p2 = plot_pd_lime(gam_model, sim_data, point, "x2", 0, FALSE, FALSE)
p3 = plot_pd_lime(gam_model, sim_data, point, "x3", 0, FALSE, FALSE)
p4 = plot_pd_lime(gam_model, sim_data, point, "x4", 0, FALSE, FALSE)

grid.arrange(p1,p2,p3,p4)

```

```{r}

point = 1
p1 = plot_pd_lime(gam_model, sim_data, point, "x1", 0, TRUE, FALSE)
p2 = plot_pd_lime(gam_model, sim_data, point, "x2", 0, TRUE, FALSE)
p3 = plot_pd_lime(gam_model, sim_data, point, "x3", 0, TRUE, FALSE)
p4 = plot_pd_lime(gam_model, sim_data, point, "x4", 0, TRUE, FALSE)

grid.arrange(p1,p2,p3,p4)


```

```{r}


point = 1
p1 = plot_pd_lime(gam_model, sim_data, point, "x1", 0.5, TRUE, FALSE)
p2 = plot_pd_lime(gam_model, sim_data, point, "x2", 0.5, TRUE, FALSE)
p3 = plot_pd_lime(gam_model, sim_data, point, "x3", 0.5, TRUE, FALSE)
p4 = plot_pd_lime(gam_model, sim_data, point, "x4", 0.5, TRUE, FALSE)

grid.arrange(p1,p2,p3,p4)

```

```{r}


point = 1
p1 = plot_pd_lime(gam_model, sim_data, point, "x1", 0.1, TRUE, TRUE)
p2 = plot_pd_lime(gam_model, sim_data, point, "x2", 0.1, TRUE, TRUE)
p3 = plot_pd_lime(gam_model, sim_data, point, "x3", 0.1, TRUE, TRUE)
p4 = plot_pd_lime(gam_model, sim_data, point, "x4", 0.1, TRUE, TRUE)

grid.arrange(p1,p2,p3,p4)

explainer = lime(sim_data,model = gam_model, bin_continuous = FALSE)
explanations = explain(sim_data[point,c("x1","x2","x3","x4")],explainer,n_features = 4)
write.table(explanations[,c("feature","feature_value","feature_weight")], "clipboard", sep="\t", row.names=FALSE)

```

```{r}


point = 500
p1 = plot_pd_lime(gam_model, sim_data, point, "x1", 0.1, TRUE, TRUE)
p2 = plot_pd_lime(gam_model, sim_data, point, "x2", 0.1, TRUE, TRUE)
p3 = plot_pd_lime(gam_model, sim_data, point, "x3", 0.1, TRUE, TRUE)
p4 = plot_pd_lime(gam_model, sim_data, point, "x4", 0.1, TRUE, TRUE)

grid.arrange(p1,p2,p3,p4)

explainer = lime(sim_data,model = gam_model, bin_continuous = FALSE)
explanations = explain(sim_data[point,c("x1","x2","x3","x4")],explainer,n_features = 4)
write.table(explanations[,c("feature","feature_value","feature_weight")], "clipboard", sep="\t", row.names=FALSE)

```

## LIME - Forest

```{r}


point = 1
p1 = plot_pd_lime(forest_model, sim_data, point, "x1", 0.1, TRUE, TRUE)
p2 = plot_pd_lime(forest_model, sim_data, point, "x2", 0.1, TRUE, TRUE)
p3 = plot_pd_lime(forest_model, sim_data, point, "x3", 0.1, TRUE, TRUE)
p4 = plot_pd_lime(forest_model, sim_data, point, "x4", 0.1, TRUE, TRUE)

grid.arrange(p1,p2,p3,p4)

explainer = lime(sim_data,model = forest_model, bin_continuous = FALSE)
explanations = explain(sim_data[point,c("x1","x2","x3","x4")],explainer,n_features = 4)
write.table(explanations[,c("feature","feature_value","feature_weight")], "clipboard", sep="\t", row.names=FALSE)

```

# Shapley Values

## Shapley Table Examples - GAM

```{r}

ex_data = sim_data[1:7,c("x1","x2","x3","x4")]
q_data = ex_data[1,]

write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)
write.table(q_data,"clipboard", sep="\t", row.names=FALSE)

ex_data$yhat = as.vector(predict(gam_model,ex_data))
mean_pred = mean(ex_data$yhat)
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)


ex_data$x1 = q_data$x1
ex_data$yhat = as.vector(predict(gam_model,ex_data))
x1_delta = mean(ex_data$yhat) - mean_pred
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)

ex_data = sim_data[1:7,c("x1","x2","x3","x4")]
ex_data$x2 = q_data$x2
ex_data$yhat = as.vector(predict(gam_model,ex_data))
x2_delta = mean(ex_data$yhat) - mean_pred
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)

ex_data$x1 = q_data$x1
ex_data$yhat = as.vector(predict(gam_model,ex_data))
x1x2_delta = mean(ex_data$yhat) - mean_pred
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)

print(x1_delta)
print(x2_delta)
print(x1x2_delta)

```

## Shapley Table Examples - Forest

```{r}

ex_data = sim_data[1:7,c("x1","x2","x3","x4")]
q_data = ex_data[1,]

write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)
write.table(q_data,"clipboard", sep="\t", row.names=FALSE)

ex_data$yhat = predict(forest_model,ex_data)
mean_pred = mean(ex_data$yhat)
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)


ex_data$x1 = q_data$x1
ex_data$yhat = predict(forest_model,ex_data)
x1_delta = mean(ex_data$yhat) - mean_pred
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)

ex_data = sim_data[1:7,c("x1","x2","x3","x4")]
ex_data$x2 = q_data$x2
ex_data$yhat = predict(forest_model,ex_data)
x2_delta = mean(ex_data$yhat) - mean_pred
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)

ex_data$x1 = q_data$x1
ex_data$yhat = predict(forest_model,ex_data)
x1x2_delta = mean(ex_data$yhat) - mean_pred
write.table(ex_data, "clipboard", sep="\t", row.names=FALSE)

print(x1_delta)
print(x2_delta)
print(x1x2_delta)

```

## Plot Shapley Values - GAM

```{r}

sim_data_x = sim_data[,c("x1","x2","x3","x4")]

shapley_line = function(model,point,feature) {

  predictor = Predictor$new(model, data=sim_data_x, y = sim_data$y)
  shapley = Shapley$new(predictor, x.interest = sim_data_x[point,], sample.size = 1000.)
  shapley_values = shapley$results

  intercept = shapley_values[shapley_values$feature == feature,"phi"][[1]]
  
  plot_domain = seq(min(sim_data[,feature]),max(sim_data[,feature]),0.1)
  exp_pred = plot_domain * 0 + intercept

  out = data.frame(feature = plot_domain, "yhat" = exp_pred)
  names(out)[names(out) == "feature"] = feature

  return(out)
}

point = 1
pred_data = sim_data
pred_data$yhat = predict(gam_model,pred_data)
p1 = partial(gam_model,pred.var = "x1", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x1",y="yhat")) +
  geom_line(data=shapley_line(gam_model, point, "x1"), aes(x1,yhat), color = "red") + 
  theme_bw(base_size = 20)

p2 = partial(gam_model,pred.var = "x2", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x2",y="yhat")) +
  geom_line(data=shapley_line(gam_model, point, "x2"), aes(x2,yhat), color = "red") + 
  theme_bw(base_size = 20)

p3 = partial(gam_model,pred.var = "x3", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x3",y="yhat")) +
  geom_line(data=shapley_line(gam_model, point, "x3"), aes(x3,yhat), color = "red") + 
  theme_bw(base_size = 20)

p4 = partial(gam_model,pred.var = "x4", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x4",y="yhat")) +
  geom_line(data=shapley_line(gam_model, point, "x4"), aes(x4,yhat), color = "red") + 
  theme_bw(base_size = 20)

grid.arrange(p1,p2,p3,p4)

predictor = Predictor$new(gam_model, data=sim_data_x, y = sim_data$y)
shapley = Shapley$new(predictor, x.interest = sim_data_x[point,], sample.size = 1000.)
shapley_values = shapley$results
write.table(shapley_values, "clipboard", sep="\t", row.names=FALSE)

```

## Plot Shapley Values - Forest

```{r}

point = 1
pred_data = sim_data
pred_data$yhat = predict(forest_model,pred_data)
p1 = partial(forest_model,pred.var = "x1", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x1",y="yhat")) +
  geom_line(data=shapley_line(forest_model, point, "x1"), aes(x1,yhat), color = "red") + 
  theme_bw(base_size = 20)

p2 = partial(forest_model,pred.var = "x2", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x2",y="yhat")) +
  geom_line(data=shapley_line(forest_model, point, "x2"), aes(x2,yhat), color = "red") + 
  theme_bw(base_size = 20)

p3 = partial(forest_model,pred.var = "x3", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x3",y="yhat")) +
  geom_line(data=shapley_line(forest_model, point, "x3"), aes(x3,yhat), color = "red") + 
  theme_bw(base_size = 20)

p4 = partial(forest_model,pred.var = "x4", plot = TRUE, plot.engine = "ggplot2") + 
  geom_point(data=pred_data[point,],aes_string(x="x4",y="yhat")) +
  geom_line(data=shapley_line(forest_model, point, "x4"), aes(x4,yhat), color = "red") + 
  theme_bw(base_size = 20)

grid.arrange(p1,p2,p3,p4)

predictor = Predictor$new(forest_model, data=sim_data_x, y = sim_data$y)
shapley = Shapley$new(predictor, x.interest = sim_data_x[point,], sample.size = 1000.)
shapley_values = shapley$results
write.table(shapley_values, "clipboard", sep="\t", row.names=FALSE)

```

















